Microplatforms: Product platforms as code

### 2018-08-22 paper.tex
Fix grammatical issues

It may seem like the only option left is to not spend the effort of building a shared platform in the first place and instead reach for a solution available in one of the cloud vendor offerings. This reduces the cost of building and scaling the platform, but the cost of sharing and the risk of lock-in stays. Furthermore, the organisation is no longer fully in control of the available tools or the way they are being used by the teams and as a result, most organisations opt for some form of governance around the cloud offering as well, which effectively leads to the same situation as the custom build in terms of coordination cost, and the limited, centrally managed set of available features. Moving to a cloud native solution seems to treat some of the symptoms of the problem, but it does not cure the underlying cause, nor does it guarantee the end result will be any more fit for purpose.

@@

With most cluster orchestration tools (e.g. Docker in Swarm mode, Kubernetes) sets of configuration, we will refer to them as “stacks” (a name used by Docker), can be deployed under an alias, which also forms a namespace for the services. Within the namespace, services can refer to each other by local names, making the entire stack portable, without any change of configuration. This gives a really light-weight mechanism for creating logical environments in a cluster.

>>>>

It may seem like the only option left is to not spend the effort of building a shared platform in the first place and instead reach for a solution available in one of the cloud vendor offerings. This reduces the cost of building and scaling the platform, but increases the cost of sharing and the risk of lock-in stays. Furthermore, the organisation is no longer fully in control of the available tools or the way they are being used by the teams and as a result, most organisations opt for some form of governance around the cloud offering as well, which effectively leads to the same situation as the custom build in terms of coordination cost, and the limited, centrally managed set of available features. Moving to a cloud native solution seems to treat some of the symptoms of the problem, but it does not cure the underlying cause, nor does it guarantee the end result will be any more fit for purpose.

@@

With most cluster orchestration tools (e.g. Docker in Swarm mode, Kubernetes), sets of configuration - we will refer to them as “stacks” (a name used by Docker) - can be deployed under an alias, which also forms a namespace for the services. Within the namespace, services can refer to each other by local names, making the entire stack portable, without any change of configuration. This gives a really light-weight mechanism for creating logical environments in a cluster.
